---
title: Neovim Sensible
output: amaryaml::github
---
```{r, setup, include = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, cache = TRUE)
```

# Introduction

Neovim's defaults are pretty good.
They are much better than Vim's at least.
But they could be improved, which is why I created this plugin.
It is inspired by [vim-sensible](https://github.com/tpope/vim-sensible), but
vim-sensible's changes are only useful to Vim users and not Neovim users because
Neovim is already more sensible than Vim.
Technically, you can use this plugin even if you are a Vim user, but it is
intended for Neovim users.
If you use Vim, I recommend installing both vim-sensible and Neovim Sensible.

# Changes

## Settings

- file encoding is set to UTF-8
- window title is enabled
- line numbering (`number` and `relativenumber`) is enabled
- `numberwidth` and `foldlevel` are set to 1
- mouse is for Vim and not the terminal
- tabs and spaces are shown with a character
- `cursorline` is enabled
- the default indentation level is set to 4 instead of 8
- `smartindent` is enabled
- `termbidi` is enabled for right-to-left language writers
- `colorcolumn` is set to equal `textwidth` + 1
- default `titlestring` is `"Neovim – %t%( %m%)"`

- do not show the hideous netrw banner

## Auto-commands

- disable marking tab and space characters for `diff` files
- disable spell-checking (if it is enabled) for `diff` and `ebuild` files
- set the `textwidth` to 50 for `gitcommit` files
- start `gitcommit` files in insert mode
- enable 24-bit colours if the terminal supports it
- set the spell-checker language to the locale's default language

## Mappings

### Completion

```{r, completion}
mode = c("Insert", "Insert")
key = c("Control-Space", "Control-L")
mapping = c("Omni complete", "Line complete")

completion = data.frame(mode, key, mapping)

kable(completion, col.name = c("Mode", "Key", "Mapping"))
```

### Clipboard

```{r, clipboard}
mode = c("Normal", "Normal", "Visual", "Visual")
key = c("Control-Y", "Control-P", "Shift-Y", "Shift-D")
mapping = c("Copy file contents to clipboard", "Paste from clipboard",
			"Copy to clipboard", "Cut to clipboard"
)

clipboard = data.frame(mode, key, mapping)

kable(clipboard, col.name = c("Mode", "Key", "Mapping"))
```

### Movement

```{r, movement}
mode = c("Insert", "Insert", "Insert")
key = c("Up", "Down", "Return")
mapping = c("Go up even when a completion menu is visible",
			"Go down even when a completion menu is visible",
			"Return even when a completion menu is visible"
)

movement = data.frame(mode, key, mapping)

kable(movement, col.name = c("Mode", "Key", "Mapping"))
```

# Installation

## Vim

```sh
`# user` git clone https://github.com/amarakon/nvim-sensible ~/.vim/pack/vendor/start/nvim-sensible
```

## Neovim

```sh
`# user` git clone https://github.com/amarakon/nvim-sensible ~/.local/share/nvim/site/pack/default/start/nvim-sensible
```
